\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects for Robust Grasp Planning Using a Multi-Armed Bandit Model with Correlated Rewards \vspace{-2ex} \versionline{14}

### 2016-02-05 ICRA2016/bandits_docs/includes/abstract.tex
Made first round of ICRA revisions, v14 of the paper

\begin{abstract}
This paper presents Dexterity Network 1.0 (Dex-Net), a new dataset and associated algorithm to study the scaling effects of Big Data and Cloud Computation on robust grasp planning. 
The algorithm uses a Multi-Armed Bandit model with correlated rewards to leverage prior grasps and 3D object models in a growing dataset that currently includes over 10,000 unique 3D object models and 2.5 million parallel-jaw grasps.
Each grasp includes an estimate of the probability of force closure under uncertainty in object and gripper pose and friction.
Dex-Net 1.0 uses Multi-View Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, as a similarity metric between objects and the Google Cloud Platform to simultaneously run up to 1,500 virtual cores, reducing runtime by three orders of magnitude.
Experiments suggest that using prior data can significantly benefit the quality and complexity of robust grasp planning.
We report on system sensitivity to varying similarity metrics and pose and friction uncertainty levels.
Code and additional information can be found at: \url{http://berkeleyautomation.github.io/dex-net/}.
\end{abstract}

>>>>

\begin{abstract}
This paper presents the Dexterity Network 1.0 (Dex-Net), a new dataset and associated algorithm to study the scaling effects of Big Data and Cloud Computation on the number of samples required for robust grasp planning. 
The algorithm uses a Multi-Armed Bandit model with correlated rewards to leverage prior grasps and 3D object models in a growing dataset that currently includes over 10,000 unique 3D object models and 2.5 million parallel-jaw grasps.
Each grasp includes an estimate of the probability of force closure under uncertainty in object and gripper pose and friction.
Dex-Net 1.0 uses Multi-View Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, as a similarity metric between objects and the Google Cloud Platform to simultaneously run up to 1,500 virtual cores, reducing experiment runtime by up to three orders of magnitude.
Experiments suggest that using prior data can significantly reduce the number of samples required to plan robust grasps.
We report on system sensitivity to varying similarity metrics and pose and friction uncertainty levels.
Code and additional information can be found at: \url{http://berkeleyautomation.github.io/dex-net/}.
\end{abstract}

### 2016-02-05 ICRA2016/bandits_docs/includes/algorithm.tex
Made first round of ICRA revisions, v14 of the paper

\section{Correlated Multi-Armed Bandit Algorithm}
\seclabel{algorithm}
The Dex-Net 1.0 algorithm (see pseudocode below) optimizes $P_F$ over a set of candidate grasps on a new object $\mO$ using Multi-Armed Bandits (MABs) with correlated rewards~\cite{hoffman2013exploiting, pandey2007multi} and priors computed from Dex-Net 1.0.
We first generate a set of candidate grasps $\Gamma$ for object $\mO$ using the antipodal grasp sampling described in \secref{grasp-sampling} and predict a prior belief distribution for each grasp using the Dex-Net database $\mD$.
Next, we run MAB by selecting a grasp using Thompson sampling~\cite{laskey2015bandits, oberlin2015autonomously}, sampling from the uncertainty random variables, determining force closure for the grasp on the sampled variables as described in \secref{quality}, and updating a belief distribution on the $P_F$ for each grasp.
Finally, we rank the grasps in $\Gamma$ by the maximum lower confidence bound of the belief distribution, a conservative estimate of the $P_F$ of each grasp, and store the ranking in the database.
We use Thompson sampling to study the scaling effects for a fixed grasp selection method and plan to study other methods based on confidence bounds~\cite{kroemer2010combining, oberlin2015autonomously} or Gittins indices~\cite{laskey2015bandits} in future work.

\subsection{Belief Distribution Model}
\seclabel{belief}
Let $\mO$ denote the test object to label with the Dex-Net Algorithm, and let $\Gamma$ be the set of $N_g$ candidate grasps generated for $\mO$.
We define $F_{j} = F(\bg_{j}) \in \{0, 1\}$ as force closure on an evaluation of any grasp $\bg_{j} \in \Gamma$ from samples of object pose, gripper pose, and friction as described in \secref{quality}.
Under the model, $F_j$ is a Bernoulli random variable with probability of success $\theta_{j}= P_F(\bg_{j})$.
Since $\theta_j$ is unknown, the algorithm maintains a posterior Beta belief distribution on the Bernoulli parameter $\theta_{j}$ that is updated with every new observation of $F$, assigning increasingly high probability to the true $P_F$. 
The Beta distribution~\cite{hoffman2013exploiting, laskey2015bandits} is specified by shape parameters $\alpha > 0$ and $\beta > 0$:

\vspace{-4ex}
\begin{align*}
	\betadist(\alpha, \beta) = Z(\alpha, \beta) \theta_j^{\alpha-1} (1 - \theta_j)^{\beta-1}
\end{align*}
\noindent where $Z(\alpha, \beta)$ is a normalization constant.

\subsection{Predicting Grasp Quality Using Prior Data}
\seclabel{ccbps}
We use Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active} to model correlations between the $P_F$ of grasps on different objects, which allows us to utilize prior grasp and object data from Dex-Net.
CCBPs model correlations between Bernoulli random variables in a Beta-Bernoulli process, which exist when the variables depend on common latent factors.
Two grasps on an object may have similar $P_F$ when they contact the object at similar locations, as evidenced by Lipschitz bounds on grasp wrench space metrics~\cite{pokorny2013c}.

A CCBP estimates the shape parameters for a grasp-object pair $\mY_{j} = (\bg_{j}, \mO_{i}) \in \mM$ using a normalized kernel function $k(\mY_p, \mY_q) : \mM \times \mM \rightarrow [0,1]$ that measures similarity between a pair of grasps and objects from the Grasp Moduli Space $\mM$.
The kernel approaches 1 as the arguments become increasingly similar and approaches 0 as the arguments become dissimilar.

We measure similarity using a set of feature maps $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., 3$, where $d_m$ is the dimension of the feature space for each.
The first feature map $\phi_{1}(\mY) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ captures similiarity in the grasp parameters, where $\bx \in \bR^3$ is the grasp center, $\bv \in \bS^2$ is the grasp approach, and $\rho_i \in \bR^3$ is the $i$-th moment arm.
To capture local surface geometry, the second feature map $\phi_{2}(\mY) = \eta(\bg, \mO)$, where $\eta$ is the differential heightmap described in \secref{grasp-similarity}.
To capture global shape information, our third feature map $\phi_{3}(\mY) = \psi(\mO)$, where $\psi$ is our object similarity map described in \secref{object-similarity}.
Given the feature maps, we use the squared exponential kernel 
\begin{align*}
	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{3} \|\phi_m(\mY_p) - \phi_m(\mY_q)\|_{C_m}^2 \right).
\end{align*}
\noindent where $C_m \in \bR^{d_m \times d_m}$ is the inverse bandwidth for $\phi_m$ and $\| \by \|_{C_m} = \by^T C_m^T C_m \by$.
The bandwidths are set by maximizing the log-likelihood~\cite{goetschalckx2011continuous} of the true $P_F$ under the CCBP on a set of training data.

We form a prior belief distribution for each candidate grasp in $\Gamma$ based on its similarity to all grasps and objects from the Dex-Net 1.0 database $\mD$ as measured by the kernel~\cite{goetschalckx2011continuous}:
%\vspace{-2ex}
\begin{align}
	%p \left(\theta_{j} | \mD \right) &= \betadist\left( \alpha_{j,0}, \beta_{j,0} \right) \notag \\
	\alpha_{j,0} = \alpha_{0} & + \sum \limits_{i=1}^{N_o} \sum \limits_{k=1}^{N_g} k(\mY_{j}, \mY_{i, k}) S_{i,k} \label{eq:alpha-prior} \\
	\beta_{j,0} = \beta_{0} & + \sum \limits_{i=1}^{N_o} \sum \limits_{k=1}^{N_g}  k(\mY_{j}, \mY_{i,k}) (N_s - S_{i,k}) \label{eq:beta-prior}
\end{align}
\noindent where $\alpha_{0}$ and $\beta_{0}$ are prior parameters for the Beta distribution~\cite{laskey2015bandits} and $N_s$ is the number of times each grasp in $\mD$ was sampled to evaluate $P_F$.
In practice, we estimate the above sums using the $N_n$ nearest neighbors to $\mO$ in the object similarity KD-Tree described in \secref{object-similarity}.
Upon observing $F_{\ell}$ for grasp $\bg_{\ell}$ on iteration $t$, we update our belief for all other grasps on object $\mO$ by~\cite{goetschalckx2011continuous}:

\vspace{-2ex}
\begin{align}
	\alpha_{j,t} &= \alpha_{j,t-1} + k(\mY_{j}, \mY_{\ell}) F_{\ell} \label{eq:alpha} \\
	\beta_{j,t} &= \beta_{j,t-1} + k(\mY_{j}, \mY_{\ell}) (1 - F_{\ell})\label{eq:beta}.
\end{align}

\begin{algorithm}
{\small
    \SetAlgoLined
    {\bf Input:} Object $\mO$, Number of Candidate Grasps $N_g$, Number of Nearest Neighbors $N_n$, Dex-Net 1.0 Database $\mD$, Features maps $\psi$ and $\eta$,  Maximum Iterations $T$, Prior beta shape $\alpha_0$, $\beta_0$, Lower Bound Confidence $p$, Random Variables $\nu$, $\xi$, and $\gamma$ \\
    \KwResult{Estimate of the grasp with highest $P_F$, $\hat{\bg}^*$}

    \tcp{Generate candidate grasps and priors}
	$\Gamma$ = AntipodalGraspSample($\mO, N_g$) \;
	$\mA_0 = \varnothing, \mB_0 = \varnothing$\;
	\For{$\bg_k \in \Gamma$}{
		\tcp{Equations~\ref{eq:alpha-prior} and ~\ref{eq:beta-prior}}
		$\alpha_{k,0}, \beta_{k,0} =$ ComputePriors($\mO, \bg_k, \mD, N_n, \psi$)\; 
		$\mA_0 = \mA_0 \cup \{\alpha_{k,0}\}, \mB_0 = \mB_0 \cup \{\beta_{k,0}\}$\;
	}

	\tcp{Run MAB to Evaluate Grasps}
	\For{$t = 1, .., T$}{
		$j = $ ThompsonSample($\mA_{t-1}, \mB_{t-1}$)\;
		$\hat{\nu}, \hat{\xi}, \hat{\gamma} =$ SampleRandomVariables($\nu, \xi, \gamma)$\;
		$F_{j} = $ EvaluateForceClosure($\bg_j, \mO, \hat{\nu}, \hat{\xi}, \hat{\gamma}$)\;
		\tcp{Equations~\ref{eq:alpha} and ~\ref{eq:beta}}
		$\mA_{t}, \mB_{t} = $ UpdateBeta($j, F_j, \Gamma$)\; 
		$\bg_{t}^* = $MaxLowerConfidence($\mA_{t}, \mB_{t}, p$)\;
	}
	return $\bg_T^*$\;
    \nonl {\bf Dex-Net 1.0 Algorithm}: Robust Grasp Planning Using Multi-Armed Bandits with Correlated Rewards
}
\end{algorithm}

>>>>

\section{Correlated Multi-Armed Bandit Algorithm}
\seclabel{algorithm}
The Dex-Net 1.0 algorithm (see pseudocode below) optimizes the probability of success $P_S$ (Equation~\ref{eq:obj}) for a binary quality metric $S$ such as force closure over a set of candidate grasps for an object $\mO$ using a Bayesian Multi-Armed Bandit (MAB) model~\cite{laskey2015bandits, srinivas10gaussian} with correlated rewards~\cite{hoffman2013exploiting, pandey2007multi} and priors computed from Dex-Net 1.0.
We first generate a set of $K$ candidate grasps, or ``arms", $\Gamma$ for object $\mO$ using the antipodal grasp sampling described in \secref{grasp-sampling}.
Next, we predict $P_S$ for each grasp using the $M$ most similar objects from the Dex-Net 1.0 dataset and estimate a Bayesian posterior distribution on our prediction.
Then, for iterations $t=1,...,T$ we use Thompson sampling~\cite{laskey2015bandits, oberlin2015autonomously} to select a grasp $\bg_{t,k} \in \Gamma$ to evaluate, sample the quality $S(\bg_{t,k})$, and update a posterior belief distribution on $P_S$ for each grasp.
Finally, we rank $\Gamma$ by the $q$-lower confidence bound on $P_S$ for each grasp and store the ranking in the database.
To illustrate convergence of the algorithm, we use force closure~\cite{zheng2005} as our binary quality metric.
We plan to study other quality metrics such as success on physical trials~\cite{kroemer2010combining, montesano2012active} and alternate MAB methods based on upper confidence bounds~\cite{kroemer2010combining, oberlin2015autonomously} or Gittins indices~\cite{laskey2015bandits} in future work.

\subsection{Model of Correlated Rewards}
\seclabel{belief}
Let $\mO$ denote the test object to label with the Dex-Net algorithm, and let $\Gamma$ be the set of $N_g$ candidate grasps generated for $\mO$.
Let $S_{j} = S(\bg_{j}) \in \{0, 1\}$ be a random binary quality metric evaluated on grasp $\bg_{j} \in \Gamma$.
For example, $S_j$ might model force closure under uncertainty in object pose, gripper pose, or friction. 
$S_j$ is a Bernoulli random variable with probability of success $\theta_{j}= P_S(\bg_{j})$.

We use Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active} to model a joint posterior belief distribution over the $\theta_j$ for all grasps in Dex-Net, which enables us to predict $\theta_j$ from prior grasp and object data in Dex-Net 1.0 using a closed-form posterior update.
The joint distribution models pairwise correlations of $P_S$ between grasp-object pairs $\mP = (\bg, \mO)$ measured using a normalized kernel function $k(\mP_i, \mP_j)$.
%Such correlations may occur between grasps contacting an object at similar locations.
The kernel approaches 1 as the arguments become increasingly similar and approaches 0 as the arguments become dissimilar.

We measure similarity using a set of feature maps $\phi_m \in \mathbb{R}^{d_m}$ for $m = 1, ..., 3$, where $d_m$ is the dimension of the feature space for each.
The first feature map $\phi_{1}(\mP) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ captures similiarity in the grasp parameters, where $\bx \in \bR^3$ is the grasp center, $\bv \in \bS^2$ is the approach axis, and $\rho_i \in \bR^3$ is the $i$-th moment arm.
To capture local surface geometry, the second feature map $\phi_{2}(\mP) = \eta(\bg, \mO)$, the differential depthmap described in \secref{grasp-similarity}.
To capture global shape information, our third feature map $\phi_{3}(\mP) = \psi(\mO)$, where $\psi$ is our object similarity map described in \secref{object-similarity}.
Given the feature maps, we use the squared exponential kernel 
\begin{align*}
	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{3} \|\phi_m(\mP_p) - \phi_m(\mP_q)\|_{C_m}^2 \right).
\end{align*}
\noindent where $C_m \in \bR^{d_m \times d_m}$ is the bandwidth for $\phi_m$ and $\| \by \|_{C_m} = \by^T C_m^{-1} \by$.
The bandwidths are set by maximizing the log-likelihood~\cite{goetschalckx2011continuous} of the true $P_S$ under the CCBP on a set of training data.

%We maintain a posterior C belief distribution~\cite{hoffman2013exploiting, laskey2015bandits} on $\theta_{j}$ based on samples of $S_j$. 
% TODO: why introduce this, put CCBP model here

%The algorithm approximately optimizes Equation~\ref{eq:obj} following the Bayesian MAB model~\cite{oberlin2015autonomously, srinivas10gaussian} by selecting a grasp $\bg_{k,t}$ on iteration $t$ from our set of ``arms" $\Gamma$ using Thompson Sampling~\cite{laskey2015bandits}, observing $S(\bg_{k,t})$, and updating a Bayesian posterior on $P_S(\bg_{k,t})$.

%The Beta distribution $\betadist(\alpha, \beta) = Z(\alpha, \beta) \theta_j^{\alpha-1} (1 - \theta_j)^{\beta-1}$, where $\alpha > 0$ and $\beta > 0$ are shape parameters and $Z(\alpha, \beta)$ is a normalization constant.
%One benefit of $\betadist$ is the closed-form updates to $\alpha$ and $\beta$ upon observing a quality evaluation $S_{j,t}$:
%TODO: closed form updates

\subsection{Predicting Grasp Quality Using Prior Data}
\seclabel{ccbps}
Before evaluating any grasps in $\Gamma$, the Dex-Net 1.0 algorithm predicts $\theta_j$ for each candidate grasp $\bg_j$ based on its kernel similarity to all grasps and objects from the Dex-Net 1.0 dataset $\mD$.
In particular, we estimate a Bayesian posterior density $p(\theta_j)$ by treating $\mD$ as prior observations and using the closed form posterior update for CCBPs~\cite{goetschalckx2011continuous}:
%\vspace{-2ex}
\begin{align}
 	p(\theta_j \mid \alpha_{j,0}, \beta_{j,0} ) &\propto \theta_j^{\alpha_{j,0}-1} (1 - \theta_j)^{\beta_{j,0}-1} \\
	\alpha_{j,0} = \alpha_{0} & + \sum \limits_{i=1}^{| \mD |} \sum \limits_{k=1}^{K} k(\mP_{j}, \mP_{i, k}) Z_{i,k} \label{eq:alpha-prior} \\
	\beta_{j,0} = \beta_{0} & + \sum \limits_{i=1}^{| \mD |} \sum \limits_{k=1}^{K}  k(\mP_{j}, \mP_{i,k}) (N - Z_{i,k}) \label{eq:beta-prior}
\end{align}
\noindent where $\alpha_{0}$ and $\beta_{0}$ are prior parameters for the Beta distribution~\cite{laskey2015bandits}, $N$ is the number of times each grasp $\bg_{i,k} \in \mD$ was sampled to estimate $\theta_i$, and $Z_{i,k}$ is the number of observed successes for $\bg_{i,k}$. 
Intuitively, the prior dataset contributes fractional observations of successes and failures for the grasp candidates $\Gamma$ proportional to the kernel similarity.
We estimate the above sums using the $M$ nearest neighbors to $\mO$ in the object similarity KD-Tree described in \secref{object-similarity}.

\subsection{Grasp Selection Policy}
On iteration $t$ we select the next grasp to sample $\bg_j \in \Gamma$ using Thompson Sampling.
In Thompson Sampling we draw a sample $\hat{\theta_{\ell}} \sim p(\theta_{\ell} \mid \alpha_{\ell,t}, \beta_{\ell,t} )$ for each grasp $\bg_{\ell} \in \Gamma$, then choose the grasp $\bg_j$ with the highest $\hat{\theta_j}$~\cite{laskey2015bandits}.
After observing $S_{j}$, we update our belief for all grasps $\bg_{\ell} \in \Gamma$ by updating a running count of the fractional successes and failures~\cite{goetschalckx2011continuous}:

\vspace{-2ex}
\begin{align}
	\alpha_{\ell,t} &= \alpha_{\ell,t-1} + k(\mP_{\ell}, \mP_{j}) S_{j} \label{eq:alpha} \\
	\beta_{\ell,t} &= \beta_{\ell,t-1} + k(\mP_{\ell}, \mP_{j}) (1 - S_{j})\label{eq:beta}.
\end{align}

\begin{algorithm}
{\small
    \SetAlgoLined
    {\bf Input:} Object $\mO$, Number of Candidate Grasps $K$, Number of Nearest Neighbors $M$, Dex-Net 1.0 Dataset $\mD$, Feature maps $\psi$ and $\eta$,  Maximum Iterations $T$, Prior beta shape $\alpha_0$, $\beta_0$, Lower Bound Confidence $q$, Quality Metric $S$ \\
    \KwResult{Estimate of the grasp with highest $P_F$, $\hat{\bg}^*$}

    \tcp{Generate candidate grasps and priors}
	$\Gamma$ = AntipodalGraspSample($\mO, K$) \;
	$\mA_0 = \varnothing, \mB_0 = \varnothing$\;
	\For{$\bg_k \in \Gamma$}{
		\tcp{Equations~\ref{eq:alpha-prior} and ~\ref{eq:beta-prior}}
		$\alpha_{k,0}, \beta_{k,0} =$ ComputePriors($\mO, \bg_k, \mD, M, \psi$)\; 
		$\mA_0 = \mA_0 \cup \{\alpha_{k,0}\}, \mB_0 = \mB_0 \cup \{\beta_{k,0}\}$\;
	}

	\tcp{Run MAB to Evaluate Grasps}
	\For{$t = 1, .., T$}{
		$j = $ ThompsonSample($\mA_{t-1}, \mB_{t-1}$)\;
		$S_{j} = $ SampleQuality($\bg_j, \mO$)\;
		\tcp{Equations~\ref{eq:alpha} and ~\ref{eq:beta}}
		$\mA_{t}, \mB_{t} = $ UpdateBeta($j, S_j, \Gamma$)\; 
		$\bg_{t}^* = $MaxLowerConfidence($q, \mA_{t}, \mB_{t}$)\;
	}
	return $\bg_T^*$\;
    \nonl {\bf Dex-Net 1.0 Algorithm}: Robust Grasp Planning Using Multi-Armed Bandits with Correlated Rewards
}
\end{algorithm}

### 2016-02-05 ICRA2016/bandits_docs/includes/conclusion.tex
Made first round of ICRA revisions, v14 of the paper

\section{Discussion and Future Work}
\seclabel{conclusion}
We presented Dexterity Network 1.0 (Dex-Net), a new dataset and associated algorithm to study the scaling effects of Big Data and Cloud Computation on robust grasp planning.
The algorithm uses a Multi-Armed Bandit model with correlated rewards to leverage prior grasps and 3D object models and Multi-View Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, as a similarity metric between objects.
In experiments, the Google Cloud Platform allowed Dex-Net 1.0 to simultaneously run up to 1,500 virtual machines, reducing experiment runtime by three orders of magnitude.
Experiments suggest that prior data can speed robust grasp planning by a factor of 2 and that average grasp quality increases with the number of similar objects in the dataset.
We reported on sensitivity to varying similarity metrics and pose and friction uncertainty levels.

In future work, we will develop metrics to pre-compute grasps that adequately "cover" each object from a variety of accessibility conditions (depending on pose and occlusions).
We will also explore how Deep Learning~\cite{krizhevsky2012imagenet} can be used in other parts of a grasp planning pipeline, for example to recognize object pose and shape from images~\cite{aubry2015understanding}, to learn grasp and object features robust to shape variation using prior evaluations from bandit algorithms, and perhaps even to determine motor torques based on images and precomputed grasps~\cite{levine2015end}.
We also hope to release subsets of Dex-Net 1.0 with an open-source API to explore robust grasping as a service (RGaaS).

>>>>

\section{Discussion and Future Work}
\seclabel{conclusion}
We presented Dexterity Network 1.0 (Dex-Net), a new dataset and associated algorithm to study the scaling effects of Big Data and Cloud Computation on robust grasp planning with binary grasp quality metrics.
The algorithm uses a Multi-Armed Bandit model with correlated rewards to leverage prior grasps and 3D object models and Multi-View Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, as a similarity metric between objects. 
In experiments, the Google Cloud Platform allowed Dex-Net 1.0 to simultaneously run up to 1,500 virtual machines, reducing experiment runtime by approximately three orders of magnitude.
Experiments suggest that prior data can speed robust grasp planning by a factor of 2 and that average grasp quality increases with the number of similar objects in the dataset.

In future work, we will develop metrics and algorithms for pre-computing a set of grasps that adequately ``cover" each object from a variety of accessibility conditions (depending on pose and occlusions).
We also plan to evaluate the Dex-Net 1.0 algorithm in physical experiments and study convergence rates when using various analytic (e.g. force closure) and simulation-based grasp quality labels from Dex-Net 1.0 to pre-predict physical grasp successes.
We will also explore Deep Learning~\cite{krizhevsky2012imagenet} to estimate grasp quality from surface depthmaps and rendered object images for further accelerating convergence.
We also hope to release subsets of Dex-Net 1.0 with an open-source API to explore robust grasping as a service (RGaaS).
